SES_Caregiving_Cognition

### 2022-03-16 SES_Caregiving_Cognition.Rmd
added figures and tables

# make sure monitoring and acceptance are on the same scale so we can compare effect sizes:
abcd.data$warmth<-(((abcd.data$warmth-1)/2)*4)+1

@@

@@

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))

# Get effect sizes
model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)

model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

# Print models to table
mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Warmth","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Warmth"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
```

@@

@@

@@

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC3.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth')
dev.off()

df.summary <- subset(abcd.data.train,!is.na(household.income)) %>%
     group_by(household.income) %>%
     summarise(
         se = sd(warmth, na.rm = TRUE)/sqrt(length(warmth)),
         warmth = mean(warmth,na.rm=TRUE))
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES.png",
    width = 4000, 
    height = 2000,
    res=700)
ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
dev.off()

df.summary <- subset(abcd.data.train,!is.na(household.income)) %>%
     group_by(household.income) %>%
     summarise(
         se = sd(monitoring, na.rm = TRUE)/sqrt(length(monitoring)),
         monitoring = mean(monitoring,na.rm=TRUE))
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES.png",
    width = 4000, 
    height = 2000,
    res=700)
ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
dev.off() 
```

@@

>>>>

# make sure monitoring and acceptance are on the same scale so we can compare effect sizes:
#abcd.data$warmth<-(((abcd.data$warmth-1)/2)*4)+1

# Replace this rescaling with z-scoring ^
abcd.data$warmth<-((abcd.data$warmth-mean(abcd.data$warmth,na.rm=TRUE))/sd(abcd.data$warmth,na.rm=TRUE))
abcd.data$monitoring<-((abcd.data$monitoring-mean(abcd.data$monitoring,na.rm=TRUE))/sd(abcd.data$monitoring,na.rm=TRUE))

@@

# Make a demographics table
```{r}
library(Gmisc)
demo_table <- abcd.data.traintest %>%
  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
#subset(matched_group<3) %>%
  set_column_labels(interview_age = "Age (Months)",
                    sex = "Sex",
                    race.6level = "Race",
                    household.income = "Household Income",
                    monitoring = "Caregiver Monitoring",
                    warmth = "Caregiver Warmth",
                    thompson_PC1 = "General Cognition",
                    thompson_PC2 = "Executive Function",
                    thompson_PC3 = "Learning/Memory",
                    high.educ = "Parent Education") %>%
getDescriptionStatsBy(interview_age, 
                        sex,
                        thompson_PC1,
                        thompson_PC2,
                        thompson_PC3,
                        monitoring,
                        warmth,
                        household.income,
                        race.6level,
                        high.educ,
                        add_total_col = TRUE, statistics=TRUE,
                        by = matched_group)

demo_table
```

@@

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))

# Get effect sizes
model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)

model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

# Print models to table
mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train)
mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train)
mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train)
mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train)
mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train)
mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train)
mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Warmth","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="numeric",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Warmth"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="numeric", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="numeric", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
```

@@

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1_violin.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_violin(aes(household.income,thompson_PC1),fill=rgb(33/255,80/255,113/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC1),width=0.2)+coord_cartesian(ylim = c(160, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
dev.off()

@@

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2_violin.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_violin(aes(household.income,thompson_PC2),fill=rgb(64/255,141/255,151/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC2),width=0.2)+coord_cartesian(ylim = c(160, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
dev.off()

@@

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3_violin.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_violin(aes(household.income,thompson_PC3),fill=rgb(157/255,207/255,160/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC3),width=0.2)+coord_cartesian(ylim = c(160, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC3.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth (z)')
dev.off()

df.summary <- subset(abcd.data.train,!is.na(household.income)) %>%
     group_by(household.income) %>%
     summarise(
         se = sd(warmth, na.rm = TRUE)/sqrt(length(warmth)),
         warmth = mean(warmth,na.rm=TRUE))
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES.png",
    width = 4000, 
    height = 2000,
    res=700)
ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
dev.off()

df.summary <- subset(abcd.data.train,!is.na(household.income)) %>%
     group_by(household.income) %>%
     summarise(
         se = sd(monitoring, na.rm = TRUE)/sqrt(length(monitoring)),
         monitoring = mean(monitoring,na.rm=TRUE))
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES.png",
    width = 4000, 
    height = 2000,
    res=700)
ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
dev.off()

save_train_data<-data.frame(abcd.data.train$thompson_PC1,abcd.data.train$thompson_PC2,abcd.data.train$thompson_PC3,abcd.data.train$warmth,abcd.data.train$monitoring)
save_test_data<-data.frame(abcd.data.test$thompson_PC1,abcd.data.test$thompson_PC2,abcd.data.test$thompson_PC3,abcd.data.test$warmth,abcd.data.test$monitoring)
write.csv(save_train_data,"/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/traintest_figs/data_from_R_train.csv")
write.csv(save_test_data,"/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/traintest_figs/data_from_R_test.csv")

@@

# Generate Figures - TEST DATA
```{r}
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1_test.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_boxplot(aes(household.income,thompson_PC1),color=rgb(33/255,80/255,113/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2_test.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_boxplot(aes(household.income,thompson_PC2),color=rgb(64/255,141/255,151/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3_test.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_boxplot(aes(household.income,thompson_PC3),color=rgb(157/255,207/255,160/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1_test.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.test,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2_test.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.test,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3_test.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.test,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1_test.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.test,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth (z)')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2_test.png",
    width = 2600, 
    height = 3100,
    res=800)
ggplot(data=abcd.data.test,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth (z)')
dev.off()
